Monte Carlo comparisons \\ VBSCAN Cost Action

### 2017-11-13 Setup/report.tex
Added pythia8 settings

>>>>

For Pythia8 this amounts to setting
\begin{verbatim}
    pythia.readString("PartonLevel:All = on"); 
    pythia.readString("HadronLevel:All = on"); 
    pythia.readString("HadronLevel:Decay = off");
    pythia.readString("PartonLevel:MPI = off"); 
    pythia.readString("BeamRemnants:primordialKT = off");
    pythia.readString("SpaceShower:QEDshowerByQ = off"); 
    pythia.readString("SpaceShower:QEDshowerByL = off"); 
    pythia.readString("TimeShower:QEDshowerByQ = off"); 
    pythia.readString("TimeShower:QEDshowerByL = off"); 
    pythia.readString("TimeShower:QEDshowerByOther = off"); 
    pythia.readString("TimeShower:QEDshowerByGamma = off"); 
    pythia.readString("Tune:pp = 14"); 
\end{verbatim}
